\normalsize \textsc{Large-Scale Data Analysis Techniques} \\ [2.0cm] \HRule{0.5pt} \\ \LARGE \textbf{\uppercase{A Review on Multi-Label Learning Algorithms}} \HRule{2pt} \\ [0.5cm] \normalsize \today \vspace*{5\baselineskip}

### 2018-01-17 Paper/PaperReport/PaperReport.tex

	This is a first-order approach algorithm, since it ignores completely any label associations. However, since the one-vs-rest scheme is used and classifiers are build for each label separately, the algorithm has the possibility of parallel implementation. Finally, the algorithm is sensitive to class-imbalance data (true positives are much less than false positives).
	%-------------------------------------------------------------------------------
	% REFERENCES
	%-------------------------------------------------------------------------------
	\newpage
	\addcontentsline{toc}{section}{Bibliography}
	\begin{thebibliography}{10}
		\bibitem{comp} 
		Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
		\bibitem{overview} Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
		\bibitem{correlations} Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
	\end{thebibliography}
\end{document}

>>>>

	This is a first-order approach algorithm, since it ignores completely any label associations. However, since the one-vs-rest scheme is used and classifiers are build for each label separately, the algorithm has the possibility of parallel implementation. Finally, the algorithm is sensitive to class-imbalance data (true positives are much less than false positives).

	\subsubsection*{Classifier Chains}
	\addcontentsline{toc}{subsubsection}{Classifier Chains}
	The logic of this algorithm is to transform the multi-label learning problem into a chain of binary classification problems, using subsequent binary classifiers in the chain, built upon the predictions of preceding ones and ordered by a permutation function. First of all, a binary training set is constructed by enriching each instance with the confidence of preceding classifiers. Moreover, a binary algorithm is used to determine whether $y_i$ label is relevant or not for an instance. For unknown instances, the algorithm predicts the relevant labels by iteratively traversing the classifier chain ($\lambda _{\tau(j)}^x \in {-1, +1}$ represents the predicted binary assignment of $y_{\tau(j)}$)

	This is a high-order method, that exploits label correlations to a degree, but in a random manner. However, it is highly sensitive to the permutation function, since the classifiers' ordering directly affects the result. One other disadvantage is that iterative operation prevents parallel implementation. Finally, one possible improvement to overcome the affect of classifiers' ordering is to use ensemble schemes.

	\subsubsection*{Claibrated Label Ranking}
	\addcontentsline{toc}{subsubsection}{Claibrated Label Ranking}
	This algorithm transforms the learning problem into a label pairwise comparison ranking problem. For $q$ labels, $q(q-1)/2$ binary classfiers are generated by pairwise comparison and a binary algorithm $g_{jk}(x)$ is used. Firstly, training sets $D_{jk}$ are constructing, where $D_{jk}: \{x_i, Y_i | y_j \in Y_i \oplus y_k \in Y_i\}$. The learning system votes for each example and if $g_{jk}(x)>0$, then $x_i$ is associated with label $y_j$, otherwise $y_j$ is irrelevant and $x_i$ is assigned to $y_k$. For unknown instances, classifiers' votes are aggregated and ranked. In addition, a virtual label $y_v$ is used as an artificial splitting point between relevant and irrelevant labels.

	This is a second-order approach algorithm using a one-vs-one scheme. The advantage of this method is that it smooths out the class-imbalance problem (where the number of a class positives is much less than the other's class positives). The disadvantage is the number of classifiers is quadratic to $|Y|$, compared to linear for Binary Relevance algorithm. One improvement to this issue is to use pruning methods to reduce the search space.

	\subsubsection*{Random k-Labelsets}
	\addcontentsline{toc}{subsubsection}{Random k-Labelsets}
	%-------------------------------------------------------------------------------
	% REFERENCES
	%-------------------------------------------------------------------------------
	\newpage
	\addcontentsline{toc}{section}{Related Work}
	\begin{thebibliography}{10}
		\bibitem{comp} 
		Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
		\bibitem{overview} Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
		\bibitem{correlations} Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
	\end{thebibliography}
\end{document}
